\Large \bf Relationship of Weather and Maize Yields in Kenya

### 2018-11-15 writing/draft1/draftMonika8.tex
kasflawbkueyfhli WORKING

{
\begin{threeparttable}
\singlespacing
\caption{\textit{\textbf{Mixed  effects model:} Log of maize yield and weather, ARMA(1,1) errors}}
%KEN11a
\label{KenARe11} 
\begin{footnotesize}

@@

\hline \vspace{-0.2cm} \\
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\vspace{0.1cm}\textbf{ }}  &\multicolumn{2}{c}{\textit{All counties}} &\multicolumn{2}{c}{\textit{ASAL}} &\multicolumn{2}{c}{\textit{non-ASAL}}\\
    \multicolumn{1}{l}{\vspace{0.1cm}\textbf{Fixed effects:}}&$exp(\beta)$&F-value%> anova(KEN11a, type='marginal')
    &$exp(\beta)$&F-value&$exp(\beta)$&F-value\\
 \hline 
\hline
\\
\vspace{-0.2cm}Intercept&$1.296$ $(1.060)^{***}$&$19.916$&$1.276$&$5.230$&$1.410^{}$&$10.061$\\
  \\
\vspace{-0.2cm}Prec. total&$1.081$ $(1.034)^{*}$&$5.402$&$1.006^{**}$&$0.022$&$1.278^{**}$&$19.386$\\
  \\
  \vspace{-0.2cm}Prec. total sq.&$0.973$ $(1.013)^{*}$&$4.289$&$1.004$&$0.051$&$0.880^{\bullet}$&$23.747$\\
    \\
      \vspace{-0.2cm}Prec. c. of var.&$0.924$ $(1.044)^{\bullet}$&$3.277$&$0.969$ &$0.246$&$0.909^{}$&$2.231$\\
  \\

         \vspace{-0.2cm}Dry spell -length&$0.935$ $(1.031)^{*}$&$4.810$&$0.833$ ${}$&$6.969$&$ 0.988^{}$&$0.163$\\
  \\
        \vspace{-0.2cm}Dry spells 	$\geq$ 4 d.&$0.939$ $(1.029)^{*}$&$4.826$&$0.855^{**}$&$8.065$&$0.989^{}$&$0.096$\\
  \\
          \vspace{-0.2cm}Temp. - average&$0.819$ $(1.059)^{***}$&$12.127$&$0.808^{*}$&$5.376$&$0.878$ $^{}$&$1.580$\\
  \\

          \vspace{-0.2cm}Temp. std. dev.&$1.043$ $(1.024)^{\bullet}$&$3.125$&$1.039$&$0.558$&$1.059$ ${*}$&$5.640$\\
  \\

  \hline
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{Random effects:}}  & \\
\vspace{-0.2cm}
\\
\hline
\\
  \vspace{-0.2cm}Intercept\\
 \\ 
 \hline
\vspace{-0.2cm} \\
\textit{Number of observations:}  &$1300$&$698$& \\
\vspace{-0.2cm}
\\

@@

>>>>

{
\begin{threeparttable}
\singlespacing
\caption{\textit{\textbf{Mixed  effects model:} Log of maize yield and weather, ARMA(1,1) errors}}
%KEN11a  KEN11a_ASAL   
\label{KenARe11} 
\begin{footnotesize}

@@

\hline \vspace{-0.2cm} \\
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\vspace{0.1cm}\textbf{ }}  &\multicolumn{2}{c}{\textit{All counties}} &\multicolumn{2}{c}{\textit{ASAL}} &\multicolumn{2}{c}{\textit{non-ASAL}}\\
    \multicolumn{1}{l}{\vspace{0.1cm}\textbf{Fixed effects:}}&$exp(\beta)$&F-value\tnote{a}%> anova(KEN11a, type='marginal')
    &$exp(\beta)$&F-value\tnote{a}&$exp(\beta)$&F-value\tnote{a}\\
 \hline 
\hline
\\
\vspace{-0.2cm}Intercept&$1.296^{***}$&$19.916$&$1.276^{*}$&$5.230$&$1.410^{**}$&$10.061$\\
  \\
\vspace{-0.2cm}Prec. total&$1.081^{*}$&$5.402$&$1.006^{}$&$0.022$&$1.278^{***}$&$19.386$\\
  \\
  \vspace{-0.2cm}Prec. total sq.&$0.973^{*}$&$4.289$&$1.004$&$0.051$&$0.880^{***}$&$23.747$\\
    \\
      \vspace{-0.2cm}Prec. c. of var.&$0.924^{\bullet}$&$3.277$&$0.969$ &$0.246$&$0.909^{}$&$2.231$\\
  \\

         \vspace{-0.2cm}Dry spell -length&$0.935^{*}$&$4.810$&$0.833^{**}$&$6.969$&$ 0.988^{}$&$0.163$\\
  \\
        \vspace{-0.2cm}Dry spells 	$\geq$ 4 d.&$0.939^{*}$&$4.826$&$0.855^{**}$&$8.065$&$0.989^{}$&$0.096$\\
  \\
          \vspace{-0.2cm}Temp. - average&$0.819^{***}$&$12.127$&$0.808^{*}$&$5.376$&$0.878$ $^{}$&$1.580$\\
  \\

          \vspace{-0.2cm}Temp. std. dev.&$1.043^{\bullet}$&$3.125$&$1.039$&$0.558$&$1.059$ ${*}$&$5.640$\\
  \\

  \hline
\vspace{-0.2cm} \\
  \multicolumn{1}{l}{\textbf{Random effects:}}  & \\
\vspace{-0.2cm}
\\
\hline
\\
  \vspace{-0.2cm}Intercept\\
 \\ 
 \hline
\vspace{-0.2cm} \\
\textit{Number of observations:}  &$1300$&$698$&$602$ \\
\vspace{-0.2cm}
\\

@@

\hline
\vspace{-0.2cm}
\end{tabular} 
\end{footnotesize}
 \begin{tablenotes}
  \begin{footnotesize}
    \item \textit{Notes:} Standard errors in brackets, \hspace{0.05cm}$1256$ observations
        \begin{adjustwidth}{1cm}{} 
    \item \hspace{0.45cm}$^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$\\
    \item[a] Marginal (type III) sum of squares. The F-statistics correspond to the sum of squares attributable to each fixed effect.
     \end{adjustwidth}
\singlespacing
  \end{footnotesize}
\end{tablenotes}
  \end{threeparttable} 
\par}
\linespread{1}
